---
geometry: left=3.8cm,right=2.5cm,top=2.5cm,bottom=2.5cm
header-includes: \usepackage{amsmath} \usepackage{pdflscape}
output:
  pdf_document:
    number_sections: yes
  html_document:
    df_print: paged
papersize: a4
---

\pagenumbering{roman}  

\newpage                 

\begin{center}       

\LARGE{NCG612 - Housing Project}

\bigskip
\bigskip

\LARGE{TODO TITLE?????}

\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip

\includegraphics[width=3in,height=3in]{NUI-Maynooth-logo.jpg}

\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip

\large{Group H}

\bigskip

\large{Haojun He}

\large{An Ning Shen}

\large{Yang Wang (19250003)}

\bigskip

\large{Description: TODO ??????}

\end{center}    

\newpage             

\tableofcontents

\newpage 

```{r echo=FALSE}
options(warn=-1)
options(scipen=200)
suppressMessages(library(ggplot2))
suppressMessages(library(maptools))
suppressMessages(library(classInt))
suppressMessages(library(RColorBrewer))
suppressMessages(library(rgdal))
suppressMessages(library(rgeos))
suppressMessages(library(MASS))
suppressMessages(library(GWmodel))
suppressMessages(library(GGally))
suppressMessages(library(car))
suppressMessages(library(tidyverse))
suppressMessages(library(gridExtra))
suppressMessages(library(cowplot))
```

\pagenumbering{arabic} 

# Introduction

Housing Valuation is an area in which statistical models can play a role. The models which are frequently
used can also be used to model other price structures.
The project is concerned with finding the most reliable determinants on property prices. 
The dataset is a subset of anonymised mortgage records for the area that is known as Greater London. The purchase price (which is different from the asking price) is available, as a a series of the characteristics of the property.
The goal is to find the best group of predictors of property price and to find the most reliable determinants on property prices. 

Describing the methods for property price prediction

  * Obtain significant predictor variables in predicting prices of housing in London

  * Obtain an estimate of the spatial variation in the influence of floorspace change on price by borough. 

  * Geographically weighted regression (GWR) is a unique type of regression. Compared to a linear regression, the predictors contributes a coefficient value which tells how much the response is changed based on a unit change in the predicting variable. Whereas in GWR, the coefficient value changes based on spatial orientation. A coefficient value is no longer global and is calculated based on that specific region. This will decrease bias and give out a more intriguing and accurate response and analysis,

# Data Preparation

## Variables in Original Dataset

```{r echo=FALSE}
LondonData <- read.csv("DataScienceProj.csv",stringsAsFactors=FALSE)
data.frame(Name=colnames(LondonData), Type=c('int','int','int','int','int','int','int','int','int','int','int','int','int','int','int','int','int','int','int','int','int','int','double','double','double','double','double','double','double','double','double'), Description=c('No.','Easting in m','Northing in m','Purchase Price in GBP','Built between 1918 and 1939','Built between 1945 and 1959','Built between 1960 and 1969','Built between 1970 and 1979','Built between 1980 and 1989','Detached property','Semi-detached property','Flat or apartment','Single Garage','Double Garage','Leasehold/Freehold indicator','Central heating','Two or more bathrooms','Two bedrooms','Three bedrooms','Four bedrooms','Fie bedrooms','New property','Floor area in square metres','Proportion of households without a car','Cars per person in neighborhood','Proportion of Households with Professional Head','Proportion of Households with Unskilled head','Proportion of residents retired','Not known','Unemployed workers','Local population density'))
```

\newpage 

## Data Cleaning

Convert dummies to factors - more convenient for modelling.

```{r echo=FALSE}
Dummy2Factor <- function(mat,lev1="Level1") {
      mat <- as.matrix(mat)
      factor((mat %*% (1:ncol(mat))) + 1,
          labels = c(lev1, colnames(mat)))
}

Age      <- Dummy2Factor(LondonData[,5:9],"PreWW1")
Type     <- Dummy2Factor(LondonData[,10:12],"Bungalow")
Garage   <- Dummy2Factor(LondonData[,13:14],"HardStnd")
Bedrooms <- Dummy2Factor(LondonData[,18:21],"BedOne")

MyData <- data.frame(LondonData[,c(2:4,15:17,22,23,26)],Age,Type,Garage,Bedrooms, LondonData[,c(24,25,27:31)])
MyData$Type<-factor(MyData$Type,levels =c("TypDetch","TypSemiD","TypFlat","Bungalow"))
MyData$CenHeat<-as.factor(MyData$CenHeat)
MyData$BathTwo<-as.factor(MyData$BathTwo)
MyData$Tenfree<-as.factor(MyData$Tenfree)
MyData$NewPropD<-as.factor(MyData$NewPropD)
```

For building model to predict the price of property in London, some variables shoud be organized properly. 

  * Age: these represent the time period in which the property was constructed. It is from variables BldIntWr,BldPostW,Bld60s,Bld70s and Bld80s. The values of it are PreWW1, BldIntWr, BldPostW, Bld60s, Bld70s and Bld80s.

  * Type: these represent the type of building. It is from variables TypDetch,TypSemiD and TypFlat. The values of it are TypDetch, TypSemiD, TypFlat and Bungalow.

  * Garage: these represent the numbers of garage that the property has. It is from variables GarSingl and GarDoubl. The values of it are HardStnd, GarSingl and GarDoubl.

  * Bedrooms: these represent the numbers of bedrooms that the property has. It is from variables BedTwo,BedThree,BedFour and BedFive. The values of it are BedOne, BedTwo, BedThree, BedFour and BedFive. 

## Variables in New Dataset.

```{r echo=FALSE}
data.frame(Name=colnames(MyData), Type=c('int','int','int','int','factor','factor','int','double','double','factor','factor','factor','factor','double','double','double','double','double','double','double'), Description=c('Easting in m','Northing in m','Purchase Price in GBP','Leasehold/Freehold indicator','Central heating','Two or more bathrooms','New property','Floor area in square metres','Proportion of Households with Professional Head','The age of building','The type of building','The Garage of building','The number of Bedrooms','Proportion of households without a car','Cars per person in neighborhood','Proportion of Households with Unskilled head','Proportion of residents retired','Not known','Unemployed workers','Local population density'))
```

\newpage 

# Data Exploration

## Exploration of Response Variable (Purprice)

```{r echo=FALSE}
p1<-ggplot(MyData, aes(y=Purprice))+ geom_boxplot() + ggtitle("Before deleting outliears")
MyData <- MyData[MyData$Purprice < 600000,]
p2<-ggplot(MyData, aes(y=Purprice))+ geom_boxplot()+ ggtitle("After deleting outliears")
plot_grid(p1, p2, labels = "AUTO")
```

Delete the outlier which is over 600,000.
The price of most property is under 600,000, but there is a outlier, which is much bigger than others. It would influence the result for the reslut of analysis.

```{r echo=FALSE}
ggplot(MyData, aes(x=FlorArea, y=Purprice))+ geom_point()+ geom_smooth(formula = y~x, method = loess, se = FALSE) + ggtitle("Purprice versus FlorArea")
```

The floor Area and price shows a somewhat linear relationship. The slope is constant and no clear curvature is present. The price increases as floor area increases.

\newpage 

## Exploration of Independent Variable (Continous Variables)

```{r echo=FALSE}
p2 <- ggplot(MyData, aes(x=ProfPct, y=Purprice))+ geom_point()+ geom_smooth(formula = y~x, method = loess, se = FALSE) + ggtitle("Purprice versus ProfPct")
p3 <- ggplot(MyData, aes(x=NoCarHh, y=Purprice))+ geom_point()+ geom_smooth(formula = y~x, method = loess, se = FALSE) + ggtitle("Purprice versus NoCarHh")
p4 <- ggplot(MyData, aes(x=CarspP, y=Purprice))+ geom_point()+ geom_smooth(formula = y~x, method = loess, se = FALSE) + ggtitle("Purprice versus CarspP")
p5 <- ggplot(MyData, aes(x=UnskPct, y=Purprice))+ geom_point()+ geom_smooth(formula = y~x, method = loess, se = FALSE) + ggtitle("Purprice versus UnskPct")

plot_grid(p2, p3, p4, p5, labels = c("A", "B", "C", "D"), ncol = 2)
```

* A: Since Profpct only takes on a few values, a linear relationship is inadequate. 

* B: TODO ??????????

* C: TODO ??????????

* D: TODO ??????????

\newpage 

```{r echo=FALSE}
p6 <- ggplot(MyData, aes(x=RetiPct, y=Purprice))+ geom_point()+ geom_smooth(formula = y~x, method = loess, se = FALSE) + ggtitle("Purprice versus RetiPct")
p7 <- ggplot(MyData, aes(x=Saleunem, y=Purprice))+ geom_point()+ geom_smooth(formula = y~x, method = loess, se = FALSE) + ggtitle("Purprice versus Saleunem")
p8 <- ggplot(MyData, aes(x=Unemploy, y=Purprice))+ geom_point()+ geom_smooth(formula = y~x, method = loess, se = FALSE) + ggtitle("Purprice versus Unemploy")
p9 <- ggplot(MyData, aes(x=PopnDnsy, y=Purprice))+ geom_point()+ geom_smooth(formula = y~x, method = loess, se = FALSE) + ggtitle("Purprice versus PopnDnsy")
plot_grid(p6, p7, p8, p9, labels = c("E", "F", "G", "H"), ncol = 2)
```

* E: TODO ??????????

* F: TODO ??????????

* G: TODO ??????????

* H: TODO ??????????

Based on the plots above, all these variables do not have string linear relationship whith dependent variable property price. For cars per person in neighborhood and proportion of households with unskilled head, the fit line almost horizontal. It means They have no liner relationship with property price. Others variables are scattered around the orgin, and most of the points are scattered tightly around the orgin. The trand of lines are mainly infuenced by outliers. The same conclusion we can get that the relationship between them and price of property are very weak.

\newpage 

## Exploration of Independent Variable (Categorical Variables)

```{r echo=FALSE}
p1 <- ggplot(MyData,aes(CenHeat,Purprice))+ geom_boxplot() + ggtitle("Purprice versus CenHeat")
p2 <- ggplot(MyData,aes(Garage,Purprice))+ geom_boxplot() + ggtitle("Purprice versus Garage")
p3 <- ggplot(MyData,aes(BathTwo,Purprice))+ geom_boxplot() + ggtitle("Purprice versus BathTwo")
p4 <- ggplot(MyData,aes(Bedrooms,Purprice))+ geom_boxplot() + ggtitle("Purprice versus Bedrooms")
plot_grid(p1, p2, p3, p4, labels = c("A", "B", "C", "D"), ncol = 2)
```


* A: It show that houses with central heating are higher priced than houses without central heating. Although the average price of houses with central heating is higher, it does not differ by a large price difference. It is more comfortable when heating is provided 24/7 as to heating which needs to be set up before using which could cause discomfort in some cases. 

* B: From the number of garages, we can clearly see that the houses with two garage’s median price is a lot higher than houses with single garage. Again, the size of the house is influenced by how many cars the garage can park. By assumption, one wouldn’t have two garages with a single room. It would only be available to houses with more than two rooms to have two garages. 

* C: Furthermore, we can see that houses with two bathrooms is also higher priced on average. This difference between one bathroom to two bathrooms is much higher. Intuitively, this would be more convenient and houses with more than one washroom are typically bigger in size based on the design of the interior. 

* D: Finally moving on to the number of bedrooms a house would have. We can see that the houses with one room and two room does not differ by much. Even three rooms doesn’t have too much difference in the median of pricing. However, as the bedroom goes to four or even five, the jump is significantly higher. 

\newpage 

```{r echo=FALSE}
p5 <- ggplot(MyData,aes(Age,Purprice))+ geom_boxplot() + ggtitle("Purprice versus Age")
p6 <- ggplot(MyData,aes(Type,Purprice))+ geom_boxplot() + ggtitle("Purprice versus Type")
plot_grid(p5, p6, labels = c("E", "F"), ncol = 2)
```

* E: Moving on the to the next predictor, we have the age of the house. From our plots, we can see that housing before the World War 1 has greatest span of pricing. It is usually because the location of the housing was excellent since it was just the beginning. Therefore, it could be one of the reasons to explain the span of prices.`

* F: The type of the house also influences the pricing of housing. For example, we had detached homes, semidetached and flats. Obviously detached homes would have the highest pricing, as it has more privacy and the layout of the houses are better. Then we have the semidetached, which is still good. However, it does lack the same amount of privacy from a full detached house. Flats would be at the end of the list since there is little privacy if the isolation was not done well. 

In the plots above, we can see that the types of property is a important factor that influence the price of a property. The property with central heating tend to be more expensive. As the number of garages, bathrooms and bedrooms goes up, the price of property shows a increase trend. However, the age of proerty seems have no influence for the price of property.Large houses clearly costs more, however as the size of the houses goes up, there are few data available. As we can see from our PurPrice vs FloorArea plot, the left size is tightly scattered with data and the right side of the line has a lot fewer data. 

\newpage 

# Fit Linear Models 

## Introduction of model

With all the predictors examined, we move to our simple linear regression model. 
We first use lm() function in R for our models. 

 * lm(Purprice~., data=MyData)

If we were to write out the function, it would be :

 * Purprice = b0 + b1*FlorArea + b2*Bedrroms + b3*Type +…+ b17*PopnDnsy

Our predictors would be able to predict the price of a house based on given London data. It would be able to predict the price based on the coefficients of the predictors. It is only required to have the right input in order to predict the price.

Then we want to find the predictor that has the most impact on price. So, we used AIC to compare the different predictors. Then fit model with all predictors and choose significant predictors for linear model. 

Finally, fit model with significan predictors and check VIF of predictors to avoid colinearity.

## Fit for A Single Variable and Look at AICs

```{r echo=FALSE}
## AIC
AICs <- rep(NA,17)
Models <- vector("list",17)
Vars <- colnames(MyData)[4:20]
## corvariance
cors <- rep(NA,17)

for(i in 1:17) {
      Models[[i]] <- lm(formula(paste0("Purprice~",Vars[i])),data=MyData)
      AICs[i] <- AIC(Models[[i]])
      if (is.integer(MyData[,i+3]) | is.double(MyData[,i+3])) {
         cors[i] <- cor(MyData$Purprice, MyData[i+3])
      }
}

## fit all by linear model
fitAll <- lm(Purprice ~ ., data=MyData[,3:20])

## AIC vs Corvariance vs VIF
x<-data.frame(name = Vars, AIC = AICs)
x[order(x$AIC),]
```

In order to choose significant variables for model, we build model  for response and every predictor respectively and output the AICs of models in the table above. We can see that the area of floor is the most important predictor for predicting the price of properties. The number of bedrooms, bathrooms and the property type are also impact the property price greatly.

\newpage 

## Fit Linear Model With All Predictors

```{r echo=FALSE}
fitAll <- lm(Purprice ~ ., data=MyData[,3:20])
summary(fitAll)
```

Then fit linear model with all predictors. The output of model shows the proportion of households without a car, cars per person in neighborhood, proportion of households with professional head, proportion of households with unskilled head, proportion of residents retired,unemployed workers,the new properties and local population density are not significant. This conclusion the the same as what we get in the corrolation coefficient table. So these variables are moved out from model.

\newpage 

## Fit Linear Model With Significant Predictors and Check VIF

```{r echo=FALSE}
fitAll_1 <- lm(Purprice ~Tenfree+CenHeat+BathTwo+FlorArea+Age+Type+Garage+Bedrooms, data=MyData)

summary(fitAll_1)
VIF<-round(vif(fitAll_1)[,1],3)
VIF
```

Buiding model with all significant predictors and check colinearity by VIF. In the table above, the colinearity of property type is very high(9.769). It shoud be moved out form model. In the next step, the dataset would be seperate into training and testing data and the linear model would be built using training dataset and be tested using testing dataset.

\newpage 

## Fit Linear Model and Test Accuracy

```{r echo=FALSE}
set.seed(1) 
## data for Linear model
lmData <- data.frame(Purprice = MyData$Purprice,
                     FlorArea = MyData$FlorArea, 
                     Bedrooms = MyData$Bedrooms, 
                     BathTwo = MyData$BathTwo, 
                     Garage = MyData$Garage, 
                     Tenfree = MyData$Tenfree, 
                     CenHeat = MyData$CenHeat, 
                     Age = MyData$Age,
                     Easting = MyData$Easting, 
                     Northing = MyData$Northing )

## training data :60% test data:40% 
s <- sample(nrow(lmData), round(.6*nrow(lmData)))
trainData <- lmData[s,]
testData <- lmData[-s,]

## fit the training data
fitTrain <- lm(Purprice~FlorArea+Bedrooms+BathTwo+Garage+Tenfree+CenHeat+Age,data=trainData)
summary(fitTrain)

## predict training data
preTrain = predict(fitTrain, trainData[,2:8])
## MSE
mean((preTrain - trainData$Purprice)^2)

## predict test data
preTest = predict(fitTrain, testData[,2:8])
## MSE
mean((preTest - testData$Purprice)^2)
```

As the output of the model above, the mean square error of testing dataset is 777827779 which is slightly lower than that of training dataset. For predictor floor area, 1 square metre increase, the average price of property would increase 715.26 GBP, keeping other predictors constant. The average price for those properties with central hesting is higer than those without central heating by 12268.51 GBP, keeping other predictors constant.

\newpage 

# Spatial Variation

## Fit model with variable Easting and Westing

```{r echo=FALSE}
x <- MyData$Easting/1000
y <- MyData$Northing/1000
m.tr2 <- lm(Purprice~x+y+I(x^2)+I(y^2)+I(x*y),data=MyData)
summary(m.tr2)
```

Fit model with variable Easting and Westing to test is the location influencing the price of properties significantly. The result shows that the properties tend to have a lower price as we move east and the infulence is significant. So it is necessary to consider the geographic effect in predicting the price of propertities. 

\newpage 

## Load Borough Data

```{r echo=FALSE}
LB <- readOGR(dsn=".", layer="LondonBoroughs",stringsAsFactors=FALSE, verbose = FALSE)  # Boroughs
LH <- SpatialPointsDataFrame(MyData[,1:2],MyData)                     # Houses
proj4string(LH) <- CRS(proj4string(LB))                               # copy CRS

LHLB <- over(LH,LB)   # spatial join: points first, then polygons
MyData$Borough <- gsub(" London Boro","",LHLB$NAME)  # get the borough name

Boroughs <- names(table(MyData$Borough))
NB <- length(Boroughs)
```

### Property Price Versus Borough

```{r echo=FALSE}
b.order <- rank(tapply(MyData$Purprice+runif(nrow(MyData)),MyData$Borough,median))

boxplot(Purprice~Borough,data=MyData,outpch=16,outcol="red",outcex=0.75,xaxt="n",at=b.order,ylim=c(0,500000))
axis(1,labels=Boroughs,at=b.order,cex.axis=0.75,las=2)
title("Property Price Versus Borough")
```

In the plot above, We can see the median of property price is diffrent in different borough in London. Expecially in the city of London, property price is significantly higher than that in other boroughs.

```{r echo=FALSE}
model.9v <- lm(Purprice~FlorArea+Bedrooms+BathTwo+Garage+Tenfree+CenHeat+Age,
               data=MyData)
MyData$stdres.9v <- stdres(model.9v)
```

\newpage 

### Standardsed Residuals Versus Borough

```{r echo=FALSE}
b.order.9v <- rank(tapply(MyData$stdres.9v+runif(nrow(MyData))*0.0001,MyData$Borough,median))
boxplot(stdres.9v~Borough,data=MyData,outpch=16,outcol="red",outcex=0.75,xaxt="n",at=b.order.9v,ylim=c(-5,5))
axis(1,labels=Boroughs,at=b.order.9v,cex.axis=0.75,las=2)
title("Standardised Residual by Borough")
abline(h=0,lty=2)
```

In the borough versus standard resudial plot, we can get the same conclusion that the distributioan of residuals in different boroughs are different. If we can fit model cansidering the effect from boroughs, the result might be better.we will now run a geographically weighted regression model to see how the coefficients of the model might vary across London.

First we will calibrate the bandwidth of the kernel that will be used to capture the points for each regression (this may take a little while) and then run the model:

\newpage 

## Geographically Weighted Regression (GWR)

### The diagnosis of model

```{r echo=FALSE}
map = SpatialPointsDataFrame(data=trainData, coords=cbind(x=trainData$Northing, y=trainData$Easting))

#bw=bw.gwr(Purprice ~ FlorArea+Bedrooms+BathTwo+Garage+Tenfree+CenHeat+Age, data=map, approach="CV",kernel="gaussian")
#save(bw, file = "bw.RData")
#bw <- 6103.785
load(file = "bw.RData")

gzesf.res<-gwr.basic(Purprice~FlorArea+Bedrooms+BathTwo+Garage+Tenfree+CenHeat+Age, data=map, bw=bw, kernel='gaussian')
#save(gzesf.res, file = "gzesf.res.Rdata")
#load(file = "gzesf.res.Rdata")
gzesf.res
```

The output from the GWR model reveals how the coefficients vary across the 33 boroughs in London. You will see how the global coefficients are exactly the same as the coefficients in the earlier linear model. In this particular model, if we take area of floor , we can see that the coefficients range from a minimum value of 612.043  GBP(1  square metre change in area of floor resulting in a increase in average price of property  of 612.043 GBP) to 821.42  GBP(1 square metre change in area of floor resulting in an increase in average price of property of 821.42 GBP). For half of the boroughs in the dataset, as floor area rises by 1 point, price of property  will increase between 676.780 GBP and 732.984 GBP(the inter-quartile range between the 1st Qu and the 3rd Qu).

\newpage 

### The diagnosis of Coefficient

The coefficient ranges can also be seen for the other variables and they suggest some interesting spatial patterning. To explore this we can plot the GWR coefficients for different variables. Firstly we can attach the coefficients to our original dataframe - this can be achieved simply as the coefficients for each ward appear in the same order in our spatial points dataframe as they do in the original dataframe.

```{r echo=FALSE}
#fortify for use in ggpplot2
boroughoutline <- fortify(LB, region="NAME")
#save(boroughoutline, file = "boroughoutline.Rdata")
#load(file = "boroughoutline.Rdata")

x <- trainData$Easting/1000
y <- trainData$Northing/1000

```

* The diagnosis of Coefficient for FlorArea, CenHeat, Bathrooms and Tenfree:

```{r echo=FALSE}
options(warn=-1)
### coefFlorArea
trainData$coefFlorArea <- gzesf.res$SDF$FlorArea
p1 <- ggplot(trainData, aes(x=x,y=y))+geom_point(aes(colour=coefFlorArea))+scale_colour_gradient2(low = "blue", mid = "white", high = "red", midpoint = (max(trainData$coefFlorArea)+ min(trainData$coefFlorArea))/2, space = "rgb", na.value = "grey50", guide = "colourbar", guide_legend(title="Coefs")) + geom_path(data=boroughoutline,aes(long/1000, lat/1000, group=id), colour="grey")+coord_equal()+ ggtitle("FlorArea") 

### coefCenHeat
trainData$coefCenHeat <- gzesf.res$SDF$CenHeat1
p2 <- ggplot(trainData, aes(x=x,y=y))+geom_point(aes(colour=coefCenHeat))+scale_colour_gradient2(low = "blue", mid = "white", high = "red", midpoint = (max(trainData$coefCenHeat)+ min(trainData$coefCenHeat))/2, space = "rgb", na.value = "grey50", guide = "colourbar", guide_legend(title="Coefs")) + geom_path(data=boroughoutline, aes(long/1000, lat/1000, group=id), colour="grey")+coord_equal() + ggtitle("CenHeat")

### coefBathTwo
## BathTwo
trainData$coefBathTwo <- gzesf.res$SDF$BathTwo1
p7 <- ggplot(trainData, aes(x=x,y=y))+geom_point(aes(colour=coefBathTwo))+scale_colour_gradient2(low = "blue", mid = "white", high = "red", midpoint = (max(trainData$coefBathTwo)+ min(trainData$coefBathTwo))/2, space = "rgb", na.value = "grey50", guide = "colourbar", guide_legend(title="Coefs")) + geom_path(data=boroughoutline, aes(long/1000, lat/1000, group=id), colour="grey")+coord_equal() + ggtitle("BathTwo")

### coefTenfree
trainData$coefTenfree <- gzesf.res$SDF$Tenfree1
p8 <- ggplot(trainData, aes(x=x,y=y))+geom_point(aes(colour=coefTenfree))+scale_colour_gradient2(low = "blue", mid = "white", high = "red", midpoint = (max(trainData$coefTenfree)+ min(trainData$coefTenfree))/2, space = "rgb", na.value = "grey50", guide = "colourbar", guide_legend(title="Coefs")) + geom_path(data=boroughoutline, aes(long/1000, lat/1000, group=id), colour="grey")+coord_equal() + ggtitle("Tenfree")

suppressWarnings(plot_grid(p1, p2, p7, p8, labels = c("A", "B", "D", "E")))
```

* A: Taking the first plot, which is for the area of floor coefficients. We can see that
in the boroughs north of the city center, there is the highest change of property price corresponding to 1 square metre increase. However, in the boroughs south of the city center, the lowest change of property price corresponding to 1 square metre increase.
This is a very interesting pattern, but may partly be explained the in the boroughs north of the city center, the buyers value the area of floor much, which makes the area of floor influencing the price of property much.

* B: The second plot is for central heating. In the west and east part of London, hasing a central heating can only influence by less than 10,000 GBP. For those boroughs in the north and south of city center, the propertity whit a center heating is much more important, the price can increase by 12,500 to 17,500 conpared with those without central heating.

* C: TODO ????????????????

* D: TODO ????????????????

\newpage 

* The diagnosis of Coefficient for Bedrooms: 

```{r echo=FALSE}
### coefBedrooms
## BedroomsBedTwo
trainData$coefBedroomsBedTwo <- gzesf.res$SDF$BedroomsBedTwo
p3 <- ggplot(trainData, aes(x=x,y=y))+geom_point(aes(colour=coefBedroomsBedTwo))+scale_colour_gradient2(low = "blue", mid = "white", high = "red", midpoint = (max(trainData$coefBedroomsBedTwo)+ min(trainData$coefBedroomsBedTwo))/2, space = "rgb", na.value = "grey50", guide = "colourbar", guide_legend(title="Coefs")) + geom_path(data=boroughoutline, aes(long/1000, lat/1000, group=id), colour="grey")+coord_equal() + ggtitle("BedroomsBedTwo") 
## BedroomsBedThree
trainData$coefBedroomsBedThree <- gzesf.res$SDF$BedroomsBedThree
p4 <- ggplot(trainData, aes(x=x,y=y))+geom_point(aes(colour=coefBedroomsBedThree))+scale_colour_gradient2(low = "blue", mid = "white", high = "red", midpoint = (max(trainData$coefBedroomsBedThree)+ min(trainData$coefBedroomsBedThree))/2, space = "rgb", na.value = "grey50", guide = "colourbar", guide_legend(title="Coefs")) + geom_path(data=boroughoutline, aes(long/1000, lat/1000, group=id), colour="grey")+coord_equal() + ggtitle("BedroomsBedThree") 
## BedroomsBedFour
trainData$coefBedroomsBedFour <- gzesf.res$SDF$BedroomsBedFour
p5 <- ggplot(trainData, aes(x=x,y=y))+geom_point(aes(colour=coefBedroomsBedFour))+scale_colour_gradient2(low = "blue", mid = "white", high = "red", midpoint = (max(trainData$coefBedroomsBedFour)+ min(trainData$coefBedroomsBedFour))/2, space = "rgb", na.value = "grey50", guide = "colourbar", guide_legend(title="Coefs")) + geom_path(data=boroughoutline, aes(long/1000, lat/1000, group=id), colour="grey")+coord_equal() + ggtitle("BedroomsBedFour") 
## BedroomsBedFive
trainData$coefBedroomsBedFive <- gzesf.res$SDF$BedroomsBedFive
p6 <- ggplot(trainData, aes(x=x,y=y))+geom_point(aes(colour=coefBedroomsBedFive))+scale_colour_gradient2(low = "blue", mid = "white", high = "red", midpoint = (max(trainData$coefBedroomsBedFive)+ min(trainData$coefBedroomsBedFive))/2, space = "rgb", na.value = "grey50", guide = "colourbar", guide_legend(title="Coefs")) + geom_path(data=boroughoutline, aes(long/1000, lat/1000, group=id), colour="grey")+coord_equal() + ggtitle("BedroomsBedFive")

suppressWarnings(plot_grid(p3, p4, p5, p6, labels = c("E-1", "E-2", "E-3", "E-4"), ncol = 2))
```

* E-1: TODO ????????????????

* E-2: TODO ????????????????

* E-3: TODO ????????????????

* E-4: TODO ????????????????

\newpage 

* The diagnosis of Coefficient for Garage: 

```{r echo=FALSE}
### coefGarage
## GarageGarSingl
trainData$coefGarageGarSingl <- gzesf.res$SDF$GarageGarSingl
p9 <- ggplot(trainData, aes(x=x,y=y))+geom_point(aes(colour=coefGarageGarSingl))+scale_colour_gradient2(low = "blue", mid = "white", high = "red", midpoint = (max(trainData$coefGarageGarSingl)+ min(trainData$coefGarageGarSingl))/2, space = "rgb", na.value = "grey50", guide = "colourbar", guide_legend(title="Coefs")) + geom_path(data=boroughoutline, aes(long/1000, lat/1000, group=id), colour="grey")+coord_equal() + ggtitle("GarSingl")
## GarageGarDoubl
trainData$coefGarageGarDoubl <- gzesf.res$SDF$GarageGarDoubl
p10 <- ggplot(trainData, aes(x=x,y=y))+geom_point(aes(colour=coefGarageGarDoubl))+scale_colour_gradient2(low = "blue", mid = "white", high = "red", midpoint =  (max(trainData$coefGarageGarDoubl)+ min(trainData$coefGarageGarDoubl))/2, space = "rgb", na.value = "grey50", guide = "colourbar", guide_legend(title="Coefs")) + geom_path(data=boroughoutline, aes(long/1000, lat/1000, group=id), colour="grey")+coord_equal() + ggtitle("GarDoubl")

suppressWarnings(plot_grid(p7, p8, labels = c("F-1", "F-2"), ncol = 2))
```

* F-1: TODO ????????????????

* F-2: TODO ????????????????

\newpage 

* The diagnosis of Coefficient for Age:

```{r echo=FALSE}
### coefAgeBldIntWr
## BldIntWr
trainData$coefAgeBldIntWr <- gzesf.res$SDF$AgeBldIntWr
p11 <- ggplot(trainData, aes(x=x,y=y))+geom_point(aes(colour=coefAgeBldIntWr))+scale_colour_gradient2(low = "blue", mid = "white", high = "red", midpoint = (max(trainData$coefAgeBldIntWr)+ min(trainData$coefAgeBldIntWr))/2, space = "rgb", na.value = "grey50", guide = "colourbar", guide_legend(title="Coefs")) + geom_path(data=boroughoutline, aes(long/1000, lat/1000, group=id), colour="grey")+coord_equal() + ggtitle("BldIntWr")
## BldPostW
trainData$coefAgeBldPostW <- gzesf.res$SDF$AgeBldPostW
p12 <- ggplot(trainData, aes(x=x,y=y))+geom_point(aes(colour=coefAgeBldPostW))+scale_colour_gradient2(low = "blue", mid = "white", high = "red", midpoint = (max(trainData$coefAgeBldPostW) + min(trainData$coefAgeBldPostW))/2, space = "rgb", na.value = "grey50", guide = "colourbar", guide_legend(title="Coefs")) + geom_path(data=boroughoutline, aes(long/1000, lat/1000, group=id), colour="grey")+coord_equal() + ggtitle("BldPostW")
## Bld60s
trainData$coefAgeBld60s <- gzesf.res$SDF$AgeBld60s
p13 <- ggplot(trainData, aes(x=x,y=y))+geom_point(aes(colour=coefAgeBld60s))+scale_colour_gradient2(low = "blue", mid = "white", high = "red", midpoint = (max(trainData$coefAgeBld60s) + min(trainData$coefAgeBld60s))/2, space = "rgb", na.value = "grey50", guide = "colourbar", guide_legend(title="Coefs")) + geom_path(data=boroughoutline, aes(long/1000, lat/1000, group=id), colour="grey")+coord_equal() + ggtitle("Bld60s")
## Bld70s
trainData$coefAgeBld70s <- gzesf.res$SDF$AgeBld70s
p14 <- ggplot(trainData, aes(x=x,y=y))+geom_point(aes(colour=coefAgeBld70s))+scale_colour_gradient2(low = "blue", mid = "white", high = "red", midpoint = (max(trainData$coefAgeBld70s) + min(trainData$coefAgeBld70s))/2, space = "rgb", na.value = "grey50", guide = "colourbar", guide_legend(title="Coefs")) + geom_path(data=boroughoutline, aes(long/1000, lat/1000, group=id), colour="grey")+coord_equal() + ggtitle("Bld70s")
## Bld80s
trainData$coefAgeBld80s <- gzesf.res$SDF$AgeBld80s
p15 <- ggplot(trainData, aes(x=x,y=y))+geom_point(aes(colour=coefAgeBld80s))+scale_colour_gradient2(low = "blue", mid = "white", high = "red", midpoint = (max(trainData$coefAgeBld80s) + min(trainData$coefAgeBld80s))/2, space = "rgb", na.value = "grey50", guide = "colourbar", guide_legend(title="Coefs")) + geom_path(data=boroughoutline, aes(long/1000, lat/1000, group=id), colour="grey")+coord_equal() + ggtitle("Bld80s")

suppressWarnings(plot_grid(p11, p12, p13, p14, p15, labels = c("G-1", "G-2", "G-3", "G-4", "G-5"), ncol = 2))
```

* G-1: TODO ????????????????

* G-2: TODO ????????????????

* G-3: TODO ????????????????

* G-4: TODO ????????????????

* G-5: TODO ????????????????

For other predictors in the model, the similar effect can also be see. They have the defferent coefficients in diffreren boroughs.

# Conclusion

In conclusion, the most reliable determinants on property prices are area of floor,the number of bedrooms, having more than two bothrooms, the number of garage, with central heating, Leasehold/Freehold indicator and the age of properties. Although,the global model with these predictors can get a good result for predicting the price of properties, it dose not consider the  spatial component. It is proved that GWR is a better way to estimate the price of property.

